%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Vicente}{Cruz}{
Santiago, Chile

\href{mailto:vcrb@uc.cl}{vcrb@uc.cl}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{German School \\ of Santiago}
\descript{High School}
\location{Dec 2018 | Santiago, CHL}
\textbf{GPA: 6.7/7.0}
\sectionsep

\subsection{Pontifical Catholic \\ University of Chile}
\descript{Engineer's Degree}
\descript{Major in Software Engineering}
\descript{Minor in Data Science}
\location{Dec 2024 | Santiago, CHL}
\textbf{GPA: 6.1/7.0} \\
\textbf{Ranking: Top 5\%}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github: \href{https://github.com/vcrb18?tab=overview&from=2022-05-01&to=2022-05-31}{\bf vcrb18} \\
LinkedIn:  \href{https://www.linkedin.com/in/vicente-cruz-866135220/}{\bf Vicente Cruz} \\
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}



\subsection{Undergraduate}
Introduction to Programming \\
Probability and Statistics\\
Advanced Programming\\
Discrete Mathematics\\
Optimization\\
Ethics\\
Microeconomics\\
Information Systems\\
Software Engineering\\
Databases\\
Data Mining\\
Technology and Web Applications\\
Detailed Design in Software\\
Visualization of Information\\
Statistical Inference\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Confident}
Python \\
\location{Familiar}
Ruby on Rails \textbullet{} Django\\
HTML \textbullet{} CSS \textbullet{} PHP \\
SQL \textbullet{} LaTeX \\
\location{Beginner}
Javascript \textbullet{} React.JS \textbullet{} Node.JS
\sectionsep

\subsection{Languages}
\location{Fluent}
Spanish \textbullet{} English \textbullet{} German



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ABOUT ME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{ABOUT ME}
Highly motivated and perseverant with a newly discovered passion for programming, software and web development.
I am convinced of self-taught learning in the computer science area and that is why I am looking for additional knowledge to what the University provides me.
Currently I dedicate several hours a week to online courses and also to read technology books and biographies of successful entrepreneurs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{\topsep}
\section{Projects}
\runsubsection{Shifts for University}
\descript{| Software Engineering Course}
\location{Mar 2022 – Jul 2022 | PUC}
\vspace{\topsep}
\begin{tightemize}
\item Developed a \textbf{web application} to organize shifts to get to and from the university.
\item Based on agile methodologies according to the \textbf{Scrum} method and worked with \textbf{Ruby on Rails, HTML/CSS} in a \textbf{4-person team} including the \textbf{product owner}.
\end{tightemize}
\sectionsep

\runsubsection{Flight Platform}
\descript{| Databases Course}
\location{Mar 20 – Jul 2022 | PUC}
\begin{tightemize}
\item Designed the \textbf{database} for a flight operational management platform.
\item Developed a website which is a platform that concentrates information related to air flights with \textbf{SQL, PHP and HTML/CSS} in a \textbf{4-person team}.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     GROUPS    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Groups} 
\runsubsection{University Athletics Team}
\descript{| 400 metres hurdles }
\location{Mar 2019 – Present | PUC}
\begin{tightemize}
\item Selected to take part in university championships.
\item Ranked in the national \textbf{top 8} in the 400 metres hurdles event.
\end{tightemize}
\sectionsep

\runsubsection{Sports Club Manquehue}
\descript{| Federated athlete}
\location{Aug 2019 - Present | Santiago}
\begin{tightemize}
\item Performed in various championships throughout the year.
\item Ranked in the national \textbf{top 8} in the 400 metres hurdles event at a federated level and \textbf{top 3} in U23.
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{\topsep}
\section{Experience}
\runsubsection{Latin American Foods}
\descript{| Packer and Laborer }
\location{Dec 2021 - Jan 2022 | Santiago}
\begin{tightemize}
\item Undertook unskilled work to get in touch with workers and so develop a critical analysis of the situation of the unskilled worker at national level.
\item Worked in \textbf{4 different areas} packaging bread, then making and packaging pizza and decorating cakes along with over \textbf{100} other workers.
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
